### 2025-06-12 paper/performance.tex
Expand.

\begin{table}
\begin{tabular}{crrr}
\textbf{Size of training set} & \multicolumn{2}{c}{\textbf{Runtime}} & \textbf{Ratio} \\
& Futhark & TensorFlow & \\
$10000$ & $0.91s$ & $1.07s$ &  $0.85\times{}$ \\
$60000$ & $4.93s$ & $2.92s$ &  $1.68\times{}$
\end{tabular}
\caption{Training time for various training set sizes, comparing
  Futhark, Tensorflow, and PyTorch, running on an A100 GPU. The final column
  shows the speedup of TensorFlow compared to Futhark. We use a batch
  size of $1000$, a training rate of $0.05$, and train for $10$
  epochs.}
\label{tab:performance}
\end{table}

>>>>

Another option is of course to generate TensorFlow, or some other established
high performance language, directly. This is in principle viable, as our overall
approach is not particularly wedded to Futhark. Extraction does become more
challenging, as \AF{E} is a \emph{pointed} higher-order
language~\cite{10.1145/3473593}, meaning programs consists of scalar expressions
nested inside parallel constructs that explicitly index arrays, while the
TensorFlow programming model uses first-order bulk parallel constructs that
implicitly operate on entire arrays at a time.

\begin{table}
\begin{tabular}{crrr}
\textbf{Size of training set} & \multicolumn{2}{c}{\textbf{Runtime}} & \textbf{Ratio} \\
& Futhark & TensorFlow & \\
$10000$ & $0.91s$ & $1.07s$ &  $0.85\times{}$ \\
$60000$ & $4.93s$ & $2.92s$ &  $1.68\times{}$
\end{tabular}
\caption{Training time for various training set sizes, comparing
  Futhark and Tensorflow, running on an A100 GPU. The final column
  shows the speedup of TensorFlow compared to Futhark. We use a batch
  size of $1000$, a training rate of $0.05$, and train for $10$
  epochs.}
\label{tab:performance}
\end{table}
